LLM Output Compliance with Handcrafted Linguistic Features --- An Experiment

### 2024-06-14 article/main.tex
more tweaks.

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            ID          & Name                    & Parameters  & Context Size & Elo Score & License Type        \\ \toprule
            gpt         & OpenAI GPT-4o           & undisclosed & 128000       & 1287      & Proprietary         \\
            gemini      & Google Gemini 1.5 Pro   & undisclosed & 1048576      & 1268      & Proprietary         \\
            claude3     & Anthropic Claude 3 Opus & undisclosed & 200000       & 1248      & Proprietary         \\
            llama3\_70b & Meta Llama 3-70B        & 70 Billion  & 8000         & 1208      & Llama 3 Community   \\
            command\_r  & Cohere Command R+       & 104 Billion & 128000       & 1189      & CC-BY-NC 4.0        \\
                        &                         &             &              &           & with Acceptable Use \\
                        &                         &             &              &           & Addendum            \\ \bottomrule
        \end{tabular}%
    }
    \caption{Large Language Model Selection}\label{table-llm}
\end{table*}

@@

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}lllll@{}}
            \toprule
            Name            & Task                     & Number of Samples & Content Type & Reference              \\ \toprule
            Yelp Reviews    & Sentiment Classification & 50000             & Reviews      & \cite{yelp2015neurips} \\
            (test split)    & Text Style Transfer      &                   &              &                        \\
                            & Text Classification      &                   &              &                        \\ \midrule
            CNN / DailyMail & Summarization            & 11490             & News         & \cite{cnndm2015}       \\
            (test split)    & Question Answering       &                   & Stories      & \cite{cnndm2017}       \\
                            & Text Generation          &                   &              &                        \\ \midrule
        \end{tabular}%
    }
    \caption{Source Datasets}\label{table-ds}
\end{table*}

>>>>

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            ID          & Name                    & Parameters  & Context Size & Elo Score & License             \\ \toprule
            gpt         & OpenAI GPT-4o           & undisclosed & 128000       & 1287      & Proprietary         \\
            gemini      & Google Gemini 1.5 Pro   & undisclosed & 1048576      & 1268      & Proprietary         \\
            claude3     & Anthropic Claude 3 Opus & undisclosed & 200000       & 1248      & Proprietary         \\
            llama3\_70b & Meta Llama 3-70B        & 70 Billion  & 8000         & 1208      & Llama 3 Community   \\
            command\_r  & Cohere Command R+       & 104 Billion & 128000       & 1189      & CC-BY-NC 4.0        \\
                        &                         &             &              &           & with Acceptable Use \\
                        &                         &             &              &           & Addendum            \\ \bottomrule
        \end{tabular}%
    }
    \caption{Large Language Model Selection}\label{table-llm}
\end{table*}

@@

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            Name            & Task                     & Number of Samples & Content Type & Reference              & License           \\ \toprule
            Yelp Reviews    & Sentiment Classification & 50000             & Reviews      &~\cite{yelp2015neurips} & Yelp Dataset      \\
            (test split)    & Text Style Transfer      &                   &              &                        & License Agreement \\
                            & Text Classification      &                   &              &                        &                   \\ \midrule
            CNN / DailyMail & Summarization            & 11490             & News         &~\cite{cnndm2015}       & Apache 2.0        \\
            (test split)    & Question Answering       &                   & Stories      &~\cite{cnndm2017}       &                   \\
                            & Text Generation          &                   &              &                        &                   \\ \bottomrule
        \end{tabular}%
    }
    \caption{Source Datasets}\label{table-ds}
\end{table*}
